---
title: "Overlap_RepetitiveElements"
author: "Yi Ding"
date: "11/15/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import overlap_summary and overlap_top9832_summary files 

The two summary files are generated by **findOverlapRepE.sh** and **top9832findOverlap.sh** on linux workstation joshuag-ux1.

Click the *Knit* button to generate a document.

```{r}
rm(list=ls(all=TRUE)) 
setwd("/Users/shding/Desktop/Peaks_JM")
x = read.table("overlap_summary.txt", sep = " ", header = F)
percentages_x = x[,1] / x[,3] * 100
x = cbind(x, percentages_x)
overlap_matrix = matrix(percentages_x, nrow = 68, ncol =7)
overlap_matrix_colnames = c("Repetitive.elements", "LINE", "LTR", "Satellite", "Simple.repeat", "SINE", "DNA.transposon")
colnames(overlap_matrix) = overlap_matrix_colnames
rownames = readLines("rowName_R_68rows.txt")
rownames_overlapMatrix = as.vector(rownames)
rownames(overlap_matrix) = rownames_overlapMatrix
#heatmap(overlap_matrix)

x.top9832 = read.table("overlap_top9832_summary.txt", sep = " ", header = F)
percent_x.top9832 = x.top9832[,1] / x.top9832[,3] * 100
x.top9832 = cbind(x.top9832, percent_x.top9832)
top9832_overlap_matrix = matrix(percent_x.top9832, nrow = 68, ncol =7)
top9832_overlap_matrix_colnames = c("Top_Repetitive.elements", "Top_LINE", "Top_LTR", "Top_Satellite", "Top_Simple.repeat", "Top_SINE", "Top_DNA.transposon")
colnames(top9832_overlap_matrix) = top9832_overlap_matrix_colnames
rownames(top9832_overlap_matrix) = rownames_overlapMatrix
overlap_includeTop9832_matrix = cbind(overlap_matrix, top9832_overlap_matrix)
#write.table(overlap_includeTop9832_matrix, file = "overlap_matrix_includeTop9832peaks.xls", sep = "\t")

i = 1
coef_Allvs.Subset = numeric(0)
while (i < length(overlap_matrix_colnames) + 1){
  res = cor(overlap_includeTop9832_matrix[,overlap_matrix_colnames[i]],overlap_includeTop9832_matrix[, top9832_overlap_matrix_colnames[i]], method = "pearson" )
  coef_Allvs.Subset[[i]] = res
  i = i + 1
}
names(coef_Allvs.Subset) = overlap_matrix_colnames
coef_Allvs.Subset
```

## Including Plots

This figure is to see the correlation relationship between all peaks and subset top 9832 peaks.

```{r ggscatter, echo=TRUE, message = FALSE}
library("ggpubr")
ggscatter(as.data.frame(overlap_includeTop9832_matrix), x = "Repetitive.elements", y = "Top_Repetitive.elements", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Overlap with Repetitive Elements", ylab = "Subset peaks overlap with Repetitive Elements")
```

Note that if you want to prevent printing of the R code that generated the plot, please use `echo = FALSE` parameter in the code chunk 
